An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-28 VLDB2026/main.tex
updata MM

	As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG achieves the best performance across all datasets. For IVF-based methods that are not specifically optimized for hybrid query scenarios (Faiss\_IVF and Milvus), their QPS remains relatively stable as the recall varies. Milvus, being a general-purpose system, exhibits comparatively poor performance. In contrast, Faiss—especially when combined with HQI\_Batch—achieves medium-level performance. Its original IVF implementation naturally supports pre-filtering and does not suffer from the complexity introduced by an increased number of attributes. In fact, filtering can reduce the effective candidate set, improving efficiency.

	The IVF-based algorithm CAPS, optimized for hybrid query scenarios, employs a multi-level partitioning strategy that introduces additional overhead. This overhead negatively impacts performan-\\ce on small datasets. However, on large datasets, the overhead is amortized, and the benefits of attribute-aware partitioning become evident, making CAPS the second-best performer after UNG.

	NHQ exhibits mediocre performance overall and performs particularly poorly on small datasets. It relies on fusion distance calculations. The fusion distance computation is highly sensitive to the number of attributes involved, thus impacting both efficiency and accuracy under multi-attribute filtering.

@@

	\begin{figure*}[htbp]
		\centering
		  \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.95\textwidth]{figures/exp/exp_8_2.pdf}
		\caption{RF-ANN search }
		\label{fig:exp_8_2}
	\end{figure*}

@@

	% \begin{figure*}[htbp]
		%     \centering
		%     \setlength{\abovecaptionskip}{0cm}
		%     \setlength{\belowcaptionskip}{-0.4cm}
		%     \includesvg[width=\textwidth]{figures/exp/exp_8_3.svg}
		%     \caption{Dataset Effect on RF-ANN Search}
		%     \label{fig:exp_8_3}
		% \end{figure*}
	\begin{figure*}[htbp]
		\centering
		    \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.8\textwidth]{figures/exp/exp_8_3.pdf}
		\caption{Dataset Effect on RF-ANN Search}
		\label{fig:exp_8_3}
	\end{figure*}

>>>>

	As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG achieves the best performance across all datasets. For IVF-based methods not specifically optimized for hybrid queries (Faiss\_IVF and Milvus), their QPS remains relatively stable as recall varies. Milvus, \textcolor{red}{as a general-purpose system}, exhibits comparatively poor performance. In contrast, Faiss—especially when combined with HQI\_Batch—achieves medium-level performance. Its original IVF implementation naturally supports pre-filtering and does not suffer from the complexity introduced by an increased number of attributes. In fact, filtering can reduce the effective candidate set, improving efficiency.
%	As shown in Figure~\ref{fig:exp_4_1_MultiLabel_1thread}, UNG achieves the best performance across all datasets. For IVF-based methods that are not specifically optimized for hybrid query scenarios (Faiss\_IVF and Milvus), their QPS remains relatively stable as the recall varies. Milvus, being a general-purpose system, exhibits comparatively poor performance. In contrast, Faiss—especially when combined with HQI\_Batch—achieves medium-level performance. Its original IVF implementation naturally supports pre-filtering and does not suffer from the complexity introduced by an increased number of attributes. In fact, filtering can reduce the effective candidate set, improving efficiency.

	The IVF-based algorithm CAPS, optimized for hybrid queries, employs a multi-level partitioning strategy that introduces additional overhead. This overhead negatively impacts performan-\\ce on small datasets. However, on large datasets, the overhead is amortized, and the benefits of attribute-aware partitioning become evident, making CAPS the second-best performer after UNG.

%	NHQ exhibits mediocre performance overall and performs particularly poorly on small datasets. It relies on fusion distance calculations. The fusion distance computation is highly sensitive to the number of attributes involved, thus impacting both efficiency and accuracy under multi-attribute filtering.
	NHQ \textcolor{red}{performs moderately overall and poorly on small datasets}. Its reliance on fusion distance computations \textcolor{red}{makes it highly sensitive to the number of attributes}, impacting both efficiency and accuracy under multi-attribute filtering.

@@

	\begin{figure*}[h]
		\centering
		\setlength{\abovecaptionskip}{0cm}
		\setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.95\textwidth]{figures/exp/exp_8_2.pdf}
		\caption{RF-ANN search }
		\label{fig:exp_8_2}
	\end{figure*}

@@

	% \begin{figure*}[htbp]
		%     \centering
		%     \setlength{\abovecaptionskip}{0cm}
		%     \setlength{\belowcaptionskip}{-0.4cm}
		%     \includesvg[width=\textwidth]{figures/exp/exp_8_3.svg}
		%     \caption{Dataset Effect on RF-ANN Search}
		%     \label{fig:exp_8_3}
		% \end{figure*}
	\begin{figure*}[htbp]
		\centering
		    \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.75\textwidth]{figures/exp/exp_8_3.pdf}
		\caption{Dataset Effect on RF-ANN Search}
		\label{fig:exp_8_3}
	\end{figure*}
